\tool

### 2018-02-08 paper/paper.tex
Intro updating

Software is becoming more and more prevalent throughout our society. To keep up with the increasing demands for technology, software engineers are making efforts to emphasize \textbf{definition}, or \textit{software quality}. Throughout the software development life cycle, more focus is being put on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}. However, despite increased attention to software quality, defects in code remains a persisting and escalating problem.

@@

To help solve the tool discovery problem among software developers, we developed \textit{\tool} to automatically recommend software engineering tools. Our system makes recommendations by integrating characteristics of peer interactions and software engineering practices. \tool~is designed for toolsmiths to increase awareness of their work by automatically running tools and making customized recommendations to developers of GitHub\footnote{https://github.com} projects. This paper seeks to answer the following research questions (RQs): \\

>>>>

Software is becoming more and more prevalent throughout our society. To keep up with the increasing demands for technology, software engineers are making efforts to emphasize \textbf{---}, or \textit{software quality}. Throughout the software development life cycle, more focus is being put on metrics that impact both software producers and consumers such as functionality, reliability, usability, efficiency, maintainability, and portability~\cite{KitchenhamQualityTarget}. However, despite increased attention to software quality, defects in code remains a persisting and escalating problem.

@@

To help solve the tool discovery problem among software engineers, we developed \textit{\tool}, a system to automatically recommend development tools. Our system makes recommendations by integrating characteristics of peer interactions and software engineering practices. \tool~is designed for toolsmiths to increase awareness of their work by automatically running tools and making customized recommendations to developers on GitHub\footnote{https://github.com} projects. This paper seeks to answer the following research questions (RQs): \\
